### 2019-12-19 README.Rmd
update readme

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```

>>>>

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/LiYingWang/kwl.pottery/master?urlpath=rstudio)

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("LiYingWang/kwl.pottery")
```
